Tail Flexibility in the Degrees of Preferential

### 2025-04-27 paper.qmd
Updating

```{r, echo=FALSE, warning=FALSE, cache=FALSE, out.width="80%"}
#| fig-width: 9
#| fig-height: 9
#| fig-cap: Posterior estimates (solid red) of survival for several real data sets and their 95% credible intervals (dotted red)
#| label: fig-real1

@@

>>>>

```{r, echo=FALSE, warning=FALSE, cache=TRUE, out.width="80%"}
#| fig-width: 9
#| fig-height: 9
#| fig-cap: Posterior estimates (solid red) of survival for several real data sets and their 95% credible intervals (dotted red)
#| label: fig-real1

@@

```{r, echo=FALSE, warning=FALSE, cache=FALSE, out.width="80%"}
#| fig-width: 9
#| fig-height: 9
#| fig-cap: df
#| label: fig-pa

plt3 = readRDS('PA_plot.rds')
plot(plt3)

```{r, echo=FALSE, warning=FALSE, cache=FALSE, out.width="80%"}
#| fig-width: 9
#| fig-height: 9
#| fig-cap: df
#| label: fig-pars

plt5 = readRDS('pars_plot.rds')
plot(plt5)
